---
title: "Bacteria only"
---
<script>
$(document).ready(function() {
  $items = $('div#TOC li');
  $items.each(function(idx) {
    num_ul = $(this).parentsUntil('#TOC').length;
    $(this).css({'text-indent': num_ul * 10, 'padding-left': 0});
  });

});
</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = FALSE, warning = FALSE}
library(data.table, warn.conflicts = FALSE)
library(igraph, warn.conflicts = FALSE)
```

`taxa` is the look-up table for the OTUs.  `cooccurrence_data` contains pairwise Spearman correlation ranks for pairs of OTUs.

```{r read_data}
taxa <- data.table(read.delim("./data/bacteria/bacteria_classified_otus"));colnames(taxa)<-c("OTU",colnames(taxa[,-1]))

head(taxa)

cooccurrence_data <- data.table(read.table("./data/bacteria/bacteria_cooccurrence", 
                                    col.names = c("treatment", "OTU_1", "OTU_2", "rho", "p")))

head(cooccurrence_data)
```

We process `coocurrence_data` by removing OTU interactions non-significant $\rho$ values by filtering out those with a $p$-value less than $0.05$, then filtering out cyanobacteria and choloroplast data, as well as all observations from bird samples:

```{r complete_data, echo = FALSE}
cooccurrence_data <- cooccurrence_data[p <= 0.05]
cooccurrence_data <- cooccurrence_data[, -5]      # Remove p-values from table
remove <- taxa[which(taxa[[4]] %in% c("Cyanobacteria","Chloroplast")),]$OTU
taxa <- taxa[-c(remove),]
complete_data <- cooccurrence_data[-c(which(apply(cooccurrence_data, 1, function(x) any(remove %in% x)))),]


bird_data <- cooccurrence_data[treatment == "Bird", ]
complete_data <- cooccurrence_data[treatment != "Bird", ]
```

We then remove all edges that are $\textit{not}$ connected to the indicated OTUs of interest:

```{r trim_data}
otus_of_interest <- c("Acinetobacter", "Gluconobacter", "Neokomagataea", "erwinia", "Pantoea", "resenbergiella", "Asaia", "Lactobacillus", "Pseudomonas")
otus_of_interest <- taxa[which(apply(taxa, 1, function(x) any(otus_of_interest %in% x))),]$OTU
trimmed_data <- complete_data[which(apply(complete_data, 1, function(x) any(otus_of_interest %in% x))), ]
head(trimmed_data)
```

We seperate the coocurrence data into a positive and negative group.

```{r}
trimmed_positive_weights <- trimmed_data[trimmed_data[['rho']] > 0]
head(trimmed_positive_weights)
```

```{r}
trimmed_negative_weights <- trimmed_data[trimmed_data[['rho']] < 0]
head(trimmed_negative_weights)
```

We'll look at the positive and negative networks for each of the three treatments, as well as when all the treatments are combined together.

# Trimmed Data

All the following analysis is performed on the trimmed data set.  Specifically, this analysis only examines interactions between *Acinetobacter, Gluconobacter, Neokomagataea, erwinia, Pantoea, resenbergiella, Asaia, Lactobacillus, Pseudomonas*

## Exposed Communities

### Positive weights 
We create a directed graph weighted by Spearman correlation for the Exposed treatment for those OTUs that are positively correlated to each other:  
```{r tep.1}
exposed_data_positive <- trimmed_positive_weights[treatment == "Exposed"]
exposed_data_positive <- exposed_data_positive[, -1]
gr_exposed_positive <- graph.data.frame(exposed_data_positive, directed = FALSE)
plot(gr_exposed_positive, vertex.size = 3,
     vertex.label.cex = 0.25)
```

To determine communities, we use `cluster_fast_greedy`, which does greedy (local) optimization of the graph's modularity score.

```{r tep.2}
exposed_communities_greedy_positive <- cluster_fast_greedy(gr_exposed_positive, weights = E(gr_exposed_positive)$rho)
plot(exposed_communities_greedy_positive, gr_exposed_positive, 
     layout = layout.fruchterman.reingold(gr_exposed_positive),
     rescaled = TRUE,
     vertex.size = 2, 
     vertex.label.cex = 0.25
     )
```

Note the community by itself.  The members of this community are:

```{r tep.3}
communities(exposed_communities_greedy_positive)[[6]]
taxa[OTU %in% communities(exposed_communities_greedy_positive)[[6]]]
```

At the center of this community is `OTU_6`:

```{r tep.4}
taxa[OTU == "OTU_6"]
```

### Negative Weights

We repeat the above process for the negatively correlated OTUs:

```{r ten.1}
exposed_data_negative <- trimmed_negative_weights[treatment == "Exposed"]
exposed_data_negative <- exposed_data_negative[, -1]
exposed_data_negative[[3]] <- abs(exposed_data_negative[[3]])
gr_exposed_negative <- graph.data.frame(exposed_data_negative, directed = FALSE)
plot(gr_exposed_negative, vertex.size = 3,
     vertex.label.cex = 0.25)
```

```{r ten.2}
exposed_communities_greedy_negative <- cluster_fast_greedy(gr_exposed_negative, weights = E(gr_exposed_negative)$rho)
plot(exposed_communities_greedy_negative, gr_exposed_negative, 
     layout = layout.fruchterman.reingold(gr_exposed_negative),
     rescaled = TRUE,
     vertex.size = 2, vertex.label.cex = 0.75)
```

We again find `OTU_6` as the center of a community.  Below are the OTUs in this community.  Notice that they are mostly $\textit{Proteobacteria}:

```{r ten.3}
taxa[OTU %in% communities(exposed_communities_greedy_negative)[[1]]]
```

Something else to note of interest is `OTU_5`, another $\textit{Proteobacteria}$:

```{r ten.4}
taxa[OTU == "OTU_5"]
```

Of interest is that `OTU_5` is in its own cluster, separate from `OTU_6`, and that there is no overlap in their own communities.  Though it is not shown here, we will see here that `OTU_5` plays a role similar to that of `OTU_6` - a highly central node in its own community.  

## Caged Communities

### Positive weights 

```{r tcp.1, echo = FALSE}
caged_data_positive <- trimmed_positive_weights[treatment == "Caged"]
caged_data_positive <- caged_data_positive[, -1]
gr_caged_positive <- graph.data.frame(caged_data_positive, directed = FALSE)
caged_communities_greedy_positive <- cluster_fast_greedy(gr_caged_positive, weights = E(gr_caged_positive)$rho)
```

```{r tcp.2}
plot(caged_communities_greedy_positive, gr_caged_positive, 
     layout = layout.fruchterman.reingold(gr_caged_positive),
     rescaled = TRUE,
     vertex.size = 2, 
     vertex.label.cex = 0.5
      )
```

We again find `OTU_6` as the central member of a cluster that is well-separated from the rest of the community.  The OTUs in this cluster are:

```{r tcp.3}
taxa[OTU %in% communities(caged_communities_greedy_positive)[[7]]]
```

### Negative Weights

```{r tcn.1}
caged_data_negative <- trimmed_negative_weights[treatment == "Caged"]
caged_data_negative <- caged_data_negative[, -1]
caged_data_negative[[3]] <- abs(caged_data_negative[[3]])
gr_caged_negative <- graph.data.frame(caged_data_negative, directed = FALSE)
caged_communities_greedy_negative <- cluster_fast_greedy(gr_caged_negative, weights = E(gr_caged_negative)$rho)
plot(caged_communities_greedy_negative, gr_caged_negative, 
     layout = layout.fruchterman.reingold(gr_caged_negative),
     rescaled = TRUE,
     vertex.size = 2, vertex.label.cex = 0.75)
```


The OTUs in the same community of `OTU_6` are:
```{r tcn.2}
taxa[OTU %in% communities(caged_communities_greedy_negative)[[2]]]
```

As mentioned above, we see `OTU_5` negatively correlated with `OTU_6` and as highly central node.  While we don't see $\textit{Proteobacteria}$ in the `OTU_6` cluster,  the OTUs in the cluster of `OTU_5` are all $\textit{Proteobacteria}$:
```{r tcn.3}
taxa[OTU %in% communities(caged_communities_greedy_negative)[[1]]]
```

## Bagged Communities

### Positive weights 

```{r tbp.1}
bagged_data_positive <- trimmed_positive_weights[treatment == "Bagged"]
bagged_data_positive <- bagged_data_positive[, -1]
gr_bagged_positive <- graph.data.frame(bagged_data_positive, directed = FALSE)
bagged_communities_greedy_positive <- cluster_fast_greedy(gr_bagged_positive, weights = E(gr_bagged_positive)$rho)
plot(bagged_communities_greedy_positive, gr_bagged_positive, 
     layout = layout.fruchterman.reingold(gr_bagged_positive),
     rescaled = TRUE,
     vertex.size = 2, 
     vertex.label.cex = 0.25
)
```

In the case of the bagged treatment, the communities aren't as well separated.  For completeness, here are the OTUs in the same community as `OTU_6`:

```{r tbp.2}
taxa[OTU %in% communities(bagged_communities_greedy_positive)[[1]]]
```

`OTU_5` was not present in this graph.
```{r}
'OTU_5' %in% V(gr_bagged_positive)$name
```

### Negative Weights

```{r tbn.1}
bagged_data_negative <- trimmed_negative_weights[treatment == "Bagged"]
bagged_data_negative <- bagged_data_negative[, -1]
bagged_data_negative[[3]] <- abs(bagged_data_negative[[3]])
gr_bagged_negative <- graph.data.frame(bagged_data_negative, directed = FALSE)
bagged_communities_greedy_negative <- cluster_fast_greedy(gr_bagged_negative, weights = E(gr_bagged_negative)$rho)
plot(bagged_communities_greedy_negative, gr_bagged_negative, 
     layout = layout.fruchterman.reingold(gr_bagged_negative),
     rescaled = TRUE,
     vertex.size = 2, vertex.label.cex = 0.75)
```

```{r tbn.2}
taxa[OTU %in% communities(bagged_communities_greedy_negative)[[1]]]
```

```{r tbn.3}
taxa[OTU %in% communities(bagged_communities_greedy_negative)[[2]]]
```
## All Treatments

We will now look at all treatments together.  Note that data points from Bird samples have already been removed.

### Positive Weights


```{r tap.1, error = TRUE}
trimmed_all_positive <- trimmed_positive_weights[, -1]
gr_trimmed_all_positive <- graph.data.frame(trimmed_all_positive, directed = FALSE)
trimmed_all_positive_communities <- cluster_fast_greedy(gr_trimmed_all_positive, 
                                    weights = E(gr_trimmed_all_positive)$rho)
```

Because all the treatments are being combined into one graph, there can be multiple (parallel) edges between OTUs.  The clustering algorithm we have been using requires that there not be multiple edges between OTUs. We will collapse multiple edges by taking their mean - that is the mean correlation of the two OTUs across all treatments. (Are there potential problems with this collapsing rule?) 

```{r tap.2}
gr_trimmed_all_positive <- simplify(gr_trimmed_all_positive, 
                                    edge.attr.comb = "mean")
trimmed_all_positive_communities <- cluster_fast_greedy(gr_trimmed_all_positive, 
                                    weights = E(gr_trimmed_all_positive)$rho)
plot(trimmed_all_positive_communities, gr_trimmed_all_positive, 
     layout = layout.fruchterman.reingold(gr_trimmed_all_positive),
     rescaled = TRUE,
     vertex.size = 2, 
     vertex.label.cex = 0.25
)
```

What's interesting here is that the graph has a lot of "spokes," which hints at important OTUs.  

### Negative Weights


```{r tan.1}
trimmed_all_negative <- trimmed_negative_weights[, -1]
trimmed_all_negative[[3]] <- abs(trimmed_all_negative[[3]])
gr_trimmed_all_negative <- graph.data.frame(trimmed_all_negative, directed = FALSE)
gr_trimmed_all_negative <- simplify(gr_trimmed_all_negative, 
                                    edge.attr.comb = "mean")
trimmed_all_negative_communities <- cluster_fast_greedy(gr_trimmed_all_negative, 
                                    weights = E(gr_trimmed_all_negative)$rho)
plot(trimmed_all_negative_communities, gr_trimmed_all_negative, 
     layout = layout.fruchterman.reingold(gr_trimmed_all_negative),
     rescaled = TRUE,
     vertex.size = 2, 
     vertex.label.cex = 0.25
)
```

`OTU_6` is again in the center of a community.  The members of that community are:

```{r, tan.2}
taxa[OTU %in% communities(trimmed_all_negative_communities)[[2]]]
```

And we see a preponderence of $\textit{proteobacteria}$.  We also see the familiar pattern with `OTU_5`.  The OTUs in this cluster are:

```{r, tan.3}
taxa[OTU %in% communities(trimmed_all_negative_communities)[[1]]]
```

# Complete Data

We reproduce the above analysis on the complete data sat.  Again, we separate the data into positive and negative networks:

```{r cd.1}
complete_positive_weights <- complete_data[complete_data[['rho']] > 0]
head(complete_positive_weights)
```

```{r cd.2}
complete_negative_weights <- complete_data[complete_data[['rho']] < 0]
head(complete_negative_weights)
```


## Exposed Communities

### Positive Weights 
```{r cep.1}
complete_exposed_positive <- complete_positive_weights[treatment == "Exposed"]
complete_exposed_positive <- complete_exposed_positive[, -1]
gr_complete_exposed_positive <- graph.data.frame(complete_exposed_positive, directed = FALSE)
complete_exposed_positive_communities <- cluster_fast_greedy(gr_complete_exposed_positive, 
                                                           weights = E(gr_complete_exposed_positive)$rho)
plot(complete_exposed_positive_communities, gr_complete_exposed_positive, 
     layout = layout.fruchterman.reingold(gr_complete_exposed_positive),
     rescaled = TRUE,
     vertex.size = 2, 
     vertex.label = NA
     )
```

### Negative Weights

```{r cen.1}
complete_exposed_negative <- complete_negative_weights[treatment == "Exposed"]
complete_exposed_negative <- complete_exposed_negative[, -1]
complete_exposed_negative[[3]] <- abs(complete_exposed_negative[[3]])
gr_complete_exposed_negative <- graph.data.frame(complete_exposed_negative, directed = FALSE)
complete_exposed_negative_communities <- cluster_fast_greedy(gr_complete_exposed_negative, 
                                                           weights = E(gr_complete_exposed_negative)$rho)
plot(complete_exposed_negative_communities, gr_complete_exposed_negative, 
     layout = layout.fruchterman.reingold(gr_complete_exposed_negative),
     rescaled = TRUE,
     vertex.size = 2, 
     vertex.label = NA
     )
```

## Caged Communities

### Positive Weights 
```{r ccp.1}
complete_caged_positive <- complete_positive_weights[treatment == "Caged"]
complete_caged_positive <- complete_caged_positive[, -1]
gr_complete_caged_positive <- graph.data.frame(complete_caged_positive, directed = FALSE)
complete_caged_positive_communities <- cluster_fast_greedy(gr_complete_caged_positive, 
                                                           weights = E(gr_complete_caged_positive)$rho)
plot(complete_caged_positive_communities, gr_complete_caged_positive, 
     layout = layout.fruchterman.reingold(gr_complete_caged_positive),
     rescaled = TRUE,
     vertex.size = 2, 
     vertex.label = NA
     )
```

### Negative Weights

```{r ccn.1}
complete_caged_negative <- complete_negative_weights[treatment == "Caged"]
complete_caged_negative <- complete_caged_negative[, -1]
complete_caged_negative[[3]] <- abs(complete_caged_negative[[3]])
gr_complete_caged_negative <- graph.data.frame(complete_caged_negative, directed = FALSE)
complete_caged_negative_communities <- cluster_fast_greedy(gr_complete_caged_negative, 
                                                           weights = E(gr_complete_caged_negative)$rho)
plot(complete_caged_negative_communities, gr_complete_caged_negative, 
     layout = layout.fruchterman.reingold(gr_complete_caged_negative),
     rescaled = TRUE,
     vertex.size = 2, 
     vertex.label.cex = 0.5
     )
```

Again, the familiar pattern.  However, `OTU_6` has lower centrality in its cluster while `OTU_5` remains highly central.  The OTUs in the `OTU_6` cluster are:

```{r, ccn.2}
taxa[OTU %in% communities(complete_caged_negative_communities)[[1]]]
```

In the `OTU_5` cluster:

```{r, ccn.3}
taxa[OTU %in% communities(complete_caged_negative_communities)[[3]]]
```

## Bagged Communities

### Positive Weights 
```{r cbp.1}
complete_bagged_positive <- complete_positive_weights[treatment == "Bagged"]
complete_bagged_positive <- complete_bagged_positive[, -1]
gr_complete_bagged_positive <- graph.data.frame(complete_bagged_positive, directed = FALSE)
complete_bagged_positive_communities <- cluster_fast_greedy(gr_complete_bagged_positive, 
                                                           weights = E(gr_complete_bagged_positive)$rho)
plot(complete_bagged_positive_communities, gr_complete_bagged_positive, 
     layout = layout.fruchterman.reingold(gr_complete_bagged_positive),
     rescaled = TRUE,
     vertex.size = 2, 
     vertex.label.cex = 0.25
     )
```

### Negative Weights
```{r cbn.1}
complete_bagged_negative <- complete_negative_weights[treatment == "Bagged"]
complete_bagged_negative <- complete_bagged_negative[, -1]
complete_bagged_negative[[3]] <- abs(complete_bagged_negative[[3]])
gr_complete_bagged_negative <- graph.data.frame(complete_bagged_negative, directed = FALSE)
complete_bagged_negative_communities <- cluster_fast_greedy(gr_complete_bagged_negative, 
                                                           weights = E(gr_complete_bagged_negative)$rho)
plot(complete_bagged_negative_communities, gr_complete_bagged_negative, 
     layout = layout.fruchterman.reingold(gr_complete_bagged_negative),
     rescaled = TRUE,
     vertex.size = 2, 
     vertex.label.cex = 0.5
     )
```
Same story as in the caged samples for the complete data.  The `OTU_6` cluster:
```{r, cbn.2}
taxa[OTU %in% communities(complete_bagged_negative_communities)[[1]]]
```

The `OTU_5` cluster:

```{r, cbn.3}
taxa[OTU %in% communities(complete_bagged_negative_communities)[[2]]]
```
## All Treatments

### Positive Weights


```{r cap.1}
complete_all_positive <- complete_positive_weights[, -1]
gr_complete_all_positive <- graph.data.frame(complete_all_positive, directed = FALSE)
gr_complete_all_positive <- simplify(gr_complete_all_positive, 
                                    edge.attr.comb = "mean")
complete_all_positive_communities <- cluster_fast_greedy(gr_complete_all_positive, 
                                    weights = E(gr_complete_all_positive)$rho)
plot(complete_all_positive_communities, gr_complete_all_positive, 
     layout = layout.fruchterman.reingold(gr_complete_all_positive),
     rescaled = TRUE,
     vertex.size = 2, 
     vertex.label.cex = 0.25
)
```



### Negative Weights


```{r, can.1}
complete_all_negative <- complete_negative_weights[, -1]
complete_all_negative[[3]] <- abs(complete_all_negative[[3]])
gr_complete_all_negative <- graph.data.frame(complete_all_negative, directed = FALSE)
gr_complete_all_negative <- simplify(gr_complete_all_negative, 
                                    edge.attr.comb = "mean")
complete_all_negative_communities <- cluster_fast_greedy(gr_complete_all_negative, 
                                    weights = E(gr_complete_all_negative)$rho)
plot(complete_all_negative_communities, gr_complete_all_negative, 
     layout = layout.fruchterman.reingold(gr_complete_all_negative),
     rescaled = TRUE,
     vertex.size = 2, 
     vertex.label.cex = 0.65
)
```
Same story, but the communities aren't as distinct.  The OTUs in the `OTU_6` cluster:

```{r, can.2}
taxa[OTU %in% communities(complete_all_negative_communities)[[2]]]
```

```{r, can.3}
taxa[OTU %in% communities(complete_all_negative_communities)[[4]]]
```

## Patristic Distance Analysis

```{r pda.1, message = FALSE, warning = FALSE}
library(ape, warn.conflicts = FALSE)
```

```{r pda.2}
rough_tree <- read.tree("./data/bacteria/bacteria_phylo_tree")
```

Generate patristic distances from `OTU_6` to use as in the paper "Phylogenetic relatedness predicts priority effects in nectar yeast communities"
```{r pda.3}
pd_matrix <- cophenetic.phylo(rough_tree)
rownames(pd_matrix) <- sub("^[^_]*_", "", rownames(pd_matrix)) 
colnames(pd_matrix) <- sub("^[^_]*_", "", colnames(pd_matrix))
otu_6.matrix <- pd_matrix["OTU_6", ]
head(otu_6.matrix)
```

# Birds

```{r}
bird_data <- bird_data[, -1]
otus_of_interest <- c("Acinetobacter", "Gluconobacter", "Neokomagataea", "erwinia", "Pantoea", "resenbergiella", "Asaia", "Lactobacillus", "Pseudomonas")
otus_of_interest <- taxa[which(apply(taxa, 1, function(x) any(otus_of_interest %in% x))),]$OTU
trimmed_bird <- bird_data[which(apply(complete_data, 1, function(x) any(otus_of_interest %in% x))),]
```

## Trimmed Data

### Positive Weights

```{r}
trimmed_bird_positive <- trimmed_bird[trimmed_bird[['rho']] > 0]
gr_trimmed_bird_positive <- graph.data.frame(trimmed_bird_positive, directed = FALSE)
gr_trimmed_bird_positive <- simplify(gr_trimmed_bird_positive, 
                                    edge.attr.comb = "mean")
trimmed_bird_positive_communities <- cluster_fast_greedy(gr_trimmed_bird_positive, 
                                    weights = E(gr_trimmed_bird_positive)$rho)
plot(trimmed_bird_positive_communities, gr_trimmed_bird_positive, 
     layout = layout.fruchterman.reingold(gr_trimmed_bird_positive),
     rescaled = TRUE,
     vertex.size = 2, 
     vertex.label.cex = 0.25
)

plot(trimmed_bird_positive_communities, gr_trimmed_bird_positive, 
     layout = layout.fruchterman.reingold(gr_trimmed_bird_positive),
     rescaled = TRUE,
     vertex.size = 2, 
     vertex.label.cex = 1,
     vertex.label = ifelse(V(gr_trimmed_bird_positive)$name == "OTU_6", 
                           V(gr_trimmed_bird_positive)$name, "")
)

adjacent_vertices(gr_trimmed_bird_positive, "OTU_6")
degree(gr_trimmed_bird_positive, "OTU_6")
```


### Negative Weights


```{r}
trimmed_bird_negative <- trimmed_bird[trimmed_bird[['rho']] < 0]
trimmed_bird_negative[[3]] <- abs(trimmed_bird_negative[[3]])
gr_trimmed_bird_negative <- graph.data.frame(trimmed_bird_negative, directed = FALSE)
gr_trimmed_bird_negative <- simplify(gr_trimmed_bird_negative, 
                                    edge.attr.comb = "mean")
trimmed_bird_negative_communities <- cluster_fast_greedy(gr_trimmed_bird_negative, 
                                    weights = E(gr_trimmed_bird_negative)$rho)
plot(trimmed_bird_negative_communities, gr_trimmed_bird_negative, 
     layout = layout.fruchterman.reingold(gr_trimmed_bird_negative),
     rescaled = TRUE,
     vertex.size = 2, 
     vertex.label.cex = 0.25
)
gr_trimmed_bird_negative
taxa[OTU %in% c("OTU_4898", "OTU_9")]
```

## Complete Data

### Positive Weights


```{r}
bird_positive <- bird_data[bird_data[['rho']] > 0]
gr_bird_positive <- graph.data.frame(bird_positive, directed = FALSE)
gr_bird_positive <- simplify(gr_bird_positive, 
                                    edge.attr.comb = "mean")
bird_positive_communities <- cluster_fast_greedy(gr_bird_positive, 
                                    weights = E(gr_bird_positive)$rho)
plot(bird_positive_communities, gr_bird_positive, 
     layout = layout.fruchterman.reingold(gr_bird_positive),
     rescaled = TRUE,
     vertex.size = 2, 
     vertex.label.cex = 0.25
)
```

### Negative Weights

```{r}
bird_negative <- bird_data[bird_data[['rho']] < 0]
bird_negative[[3]] <- abs(bird_negative[[3]])
gr_bird_negative <- graph.data.frame(bird_negative, directed = FALSE)
gr_bird_negative <- simplify(gr_bird_negative, 
                                    edge.attr.comb = "mean")
bird_negative_communities <- cluster_fast_greedy(gr_bird_negative, 
                                    weights = E(gr_bird_negative)$rho)
plot(bird_negative_communities, gr_bird_negative, 
     layout = layout.fruchterman.reingold(gr_bird_negative),
     rescaled = TRUE,
     vertex.size = 2, 
     vertex.label.cex = 0.25
)
```