---
title: "Differential Abundance Analysis of Bacteria"
---
<script>
$(document).ready(function() {
  $items = $('div#TOC li');
  $items.each(function(idx) {
    num_ul = $(this).parentsUntil('#TOC').length;
    $(this).css({'text-indent': num_ul * 10, 'padding-left': 0});
  });
});
</script>

```{r, message = FALSE, warning = FALSE}
.cran_packages <- c("data.table", "igraph", "ggplot2", "RColorBrewer", "vegetarian", "vegan", "knitr");.inst <- .cran_packages %in% installed.packages();if(any(!.inst)) {install.packages(.cran_packages[!.inst])};.bioc_packages <- c("DESeq2","phyloseq"); if(any(!.inst)){source("http://bioconductor.org/biocLite.R");biocLite(.bioc_packages[!.inst], ask = F)}; sapply(c(.cran_packages, .bioc_packages), require, character.only = TRUE); 

```

```{r load-data}
phylo.data <- readRDS("data/bacteria/germs_otus/bacteria_phyloseq.rds")
phylo.data <- prune_samples(sample_sums(phylo.data)>=100, phylo.data)
phylo.data <- filter_taxa(phylo.data, function(x) sum(x) >= 5, T)
```

```{r gather-data}
abundances <- as.matrix(otu_table(phylo.data))
metadata <- sample_data(phylo.data)
experiment <- ~ Flower
```

```{r normalization}
rarecurve(abundances, step = 20, sample = min(rowSds(abundances)), xlab = "Sample Size", ylab = "Species", label = TRUE)
rarecurve(abundances, step = 20, sample = 5, xlab = "Sample Size", ylab = "Species", label = TRUE)
```

```{r DESeq}
dds <- DESeqDataSetFromMatrix(countData = abundances, colData = metadata, design = experiment)

```


dds
# class: DESeqDataSet
# dim: 4321 48
# metadata(1): version
# assays(1): counts
# rownames(4321): b0001 b0002 ... pJMY_bla pJMY_lacI
# rowData names(0):
# colnames(48): MLC115_Empty_6hr_1 MLC115_Empty_6hr_2 ... LAR1_TE_24hr_3 LAR1_TE_24hr_4
# colData names(3): strain plasmid time

## Specify reference levels
## Default is alphabetical, see time factor:
levels(dds$time)
# [1] "12hr" "24hr" "6hr"

## Follow order in data files
dds$strain <- factor(dds$strain,levels=unique(colData[,1]))
dds$plasmid <- factor(dds$plasmid,levels=unique(colData[,2]))
dds$time <- factor(dds$time,levels=unique(colData[,3]))

## Now, 6hr is the reference level:
levels(dds$time)
# [1] "6hr"  "12hr" "24hr"

## Add metadata to dds object
(mcols(dds) <- DataFrame(mcols(dds), Rockhopper_meta))
# DataFrame with 4321 rows and 2 columns
#                        Name                                               Product
#                    <factor>                                              <factor>
# b0001                  thrL                             thr operon leader peptide
# b0002                  thrA Bifunctional aspartokinase/homoserine dehydrogenase 1
# ...

### Run DESeq ###
dds_full <- DESeq(dds)
# estimating size factors
# estimating dispersions
# gene-wise dispersion estimates
# mean-dispersion relationship
# final dispersion estimates
# fitting model and testing

## Save DESeq2 normalized expression to CSV
DESeq2_norm <- counts(dds_full, normalized=TRUE)
write.csv(as.data.frame(DESeq2_norm), file="DESeq2_norm.csv", collapse=""))


### Testing for significance ###
# See section 3.3: Interactions

## Add a "group" factor which is a combinations of original factors
dds_group <- dds
dds_group$group <- factor(sub("_[0-9]$","",rownames(colData)))
## Relevel
dds_group$group <- factor(dds_group$group, levels=unique(dds_group$group))
## Reset design
design(dds_group) <- ~ group
## Rerun DESeq2 using only 'group' as the model
dds_group <- DESeq(dds_group)
resultsNames(dds_group)
#  [1] "Intercept"              "groupMLC115_Empty_6hr"  "groupMLC115_Empty_12hr" "groupMLC115_Empty_24hr"
#  [5] "groupMLC115_TE_6hr"     "groupMLC115_TE_12hr"    "groupMLC115_TE_24hr"    "groupLAR1_Empty_6hr"
#  [9] "groupLAR1_Empty_12hr"   "groupLAR1_Empty_24hr"   "groupLAR1_TE_6hr"       "groupLAR1_TE_12hr"
# [13] "groupLAR1_TE_24hr"


## Compare with...
resultsNames(dds_full)
# [1] "Intercept"                     "strain_LAR1_vs_MLC115"         "plasmid_TE_vs_Empty"
# [4] "time_12hr_vs_6hr"              "time_24hr_vs_6hr"              "strainLAR1.plasmidTE"
# [7] "strainLAR1.time12hr"           "strainLAR1.time24hr"           "plasmidTE.time12hr"
# [10] "plasmidTE.time24hr"            "strainLAR1.plasmidTE.time12hr" "strainLAR1.plasmidTE.time24hr"