---
title: "Creating Cooccurrence for our Bacteria OTUs"
---

```{r setup, include=FALSE}
set.seed(1390)
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, message = FALSE, warning = FALSE}
library(phyloseq, warn.conflicts = FALSE)
```

The otu tables were made in our pipeline using cd-hit to call clusters (OTUS) and custom scripts for formatting the table.

```{r load_data}
otus <- read.table("../data/bacteria/germs_otus/bac_cdhit_otu_table_wide.txt", header=TRUE, row.names=1)
quantile(colSums(otus))
sum(colSums(otus) < 100)/ ncol(otus)
otus <- otus[,colSums(otus) >= 5]
```

## Combining OTU data with Taxonomy

Taxonomy classifications were done using the rdp-classifier program.

```{r add_info}
tax <- read.delim("../data/bacteria/germs_otus/bac_cdhit_taxa_table_w_repseq.txt", row.names=1)
```

## Sample Data

Sample names were numerical, which R does not accept, and so an 'X' was prepended to each by R, and I kept that nomenclature.

```{r}
si <- read.csv("../data/bacteria/Data_for_bacterial_OTUs.csv")[,-1]
time_data <- read.csv("../data/bacteria/bac_time_data.csv", header = TRUE, row.names = 1); rownames(time_data) <- paste("X",rownames(time_data), sep = "")
colnames(si) <- c("Flower", "Treatment", "sample.name")
rownames(si) <- paste("X", si$Flower, sep="")
si <- merge(si,time_data["Month"],by="row.names",all.x=TRUE), rownames(si)<-si$Row.names;si<-subset(si, select=-c(Row.names))
```

## Creating Phyloseq Objects
```{r phyloseq, message=FALSE}
phylo <- phyloseq(otu_table(as.matrix(otus), taxa_are_rows=T), tax_table(as.matrix(tax)), sample_data(si))
phylo <- subset_taxa(phylo, class != "Cyanobacteria")
phylo <- subset_taxa(phylo, class != "Chloroplast")
phylo <- subset_taxa(phylo, phylum != "unclassified_Bacteria")
phylo <- prune_taxa(taxa_sums(phylo) > ncol(otu_table(phylo))*.1 , phylo)
phylo
```

Whether or not rareficaiton is the correct choice, we may need to look at in the future.

```{r rarefy, message=FALSE}
# phylo <- rarefy_even_depth(phylo, sample.size = 500)
saveRDS(phylo,"../data/bacteria/germs_otus/bacteria_phyloseq.rds")
```

## Co-Ocurrence

Cooccurrence is run in and outside program, written in C++ by a member of out lab. It uses Spearman's rank correlation and requires a specific input style created here.

```{r co_ocurrence}
trt <- as.character(sample_data(phylo)$Treatment)
f_table <- cbind(trt, t(otu_table(phylo)))
write.csv(f_table, "../data/bacteria/germs_otus/bac_fcoocurr_input.csv")
```

